HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex

\begin{tikzpicture}[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [fill=black, circle] {}
  child {node {After} edge from parent node[left]  {$L$\hspace{1.5cm}}}
  child {node (H1)  [fill=black,circle] {}
    child {node {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2)  [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node  (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node  {moved} edge from parent node[right] {$P$}}
      child {node  [fill=black,circle] {}
        child {node  {to} edge from parent node[right] {$R$}}
        child {node  {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
  \end{tikzpicture}
\caption{\label{fig:ucca_example}
  Sample UCCA annotation. Edge labels mark UCCA categories. }
\end{figure}

@@

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}.
Let $L$ be the set of possible UCCA labels.
Given a sentence $s = (w_1, \ldots,w_n)$, its UCCA annotation is a DAG $G=(V,E,\ell)$,
where $\ell: V \rightarrow L$, and where $W = \{w_1,\ldots,w_n\}$ correspond to the leaves of $G$.
For every node $v \in V$, we define its {\it yield} $yld(v)$ as $v$'s descendants in $W$.
The semantic units for a sentence $s$ induced by the annotation $G$,
is the set of yields of nodes in $V$. %We denote it with $Units(s)$ for brevity.
We note that the translation is not UCCA-annotated.

\begin{figure*}[t]
    \includegraphics[width=1\textwidth]{ucca-tree-mteval.jpg}
    \caption{UCCA Tree evaluated in comparison to an aligned ``translation'' (an
	English paraphrase).}
    \label{fig:ucca-tree-hume}
\end{figure*}

\paragraph{Translation Evaluation.}
The basic strategy for computing HUME is to traverse
the semantic units of the source sentence, and to mark the extent to which
they have been correctly translated. As semantic units correspond to the
semantic relations expressed in the text and the inter-relations between them,
HUME effectively aggregates the judgements of the users into a composite score.

>>>>

\begin{tikzpicture}[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [fill=black, circle] {}
  child {node {After} edge from parent node[left]  {$L$\hspace{1.5cm}}}
  child {node (H1)  [fill=black,circle] {}
    child {node {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2)  [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node  (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node  {moved} edge from parent node[right] {$P$}}
      child {node  [fill=black,circle] {}
        child {node  {to} edge from parent node[right] {$R$}}
        child {node  {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
  \end{tikzpicture}
\caption{\label{fig:ucca_example}
  Sample UCCA annotation of the sentence ``After graduation, Tom moved
  to NYC''. Leaves correspond to words, whereas nodes correspond to units.
  Edge labels mark UCCA categories, which are largely ignored in this work.}
\end{figure}

@@

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}.
Let $L$ be the set of possible UCCA labels.
Given a sentence $s = (w_1, \ldots,w_n)$, its UCCA annotation is a DAG $G=(V,E,\ell)$,
where $\ell: V \rightarrow L$, and where $W = \{w_1,\ldots,w_n\}$ correspond to the leaves of $G$.
For every node $v \in V$, we define its {\it yield} $yld(v)$ as $v$'s descendants in $W$.
The semantic units for a sentence $s$ according to $G$
is the set of yields of nodes in $V$. 
We note that the translation is not UCCA-annotated.

%\begin{figure*}[t]
%    \includegraphics[width=1\textwidth]{ucca-tree-mteval.jpg}
%    \caption{UCCA Tree evaluated in comparison to an aligned ``translation'' (an
%	English paraphrase).}
%    \label{fig:ucca-tree-hume}
%\end{figure*}

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
%  \begin{tikzpicture}
%    [level 1/.style={sibling distance=7.5em},
%      level 2/.style={sibling distance=5em},
%      level 3/.style={sibling distance=5em},
%      level 4/.style={sibling distance=3em}]
%    %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
%    %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
%  \node (ROOT) [label={B}] [fill=blue, circle] {}
%  child {node (H3) [label={A}] [fill=yellow,circle] {}
%    child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
%    child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
%      child {node [label={}] {became} edge from parent node[left]  {}}
%      child {node [label={}] {a} edge from parent node[left]  {}}
%      child {node [label={}] {passion} edge from parent node[left]  {}}
%    }
%    child {node (H2) [label={A}] [fill=yellow,circle] {}
%      child {node {} edge from parent[draw=none] {}}
%      child {node {} edge from parent[draw=none] {}}
%      child {node {} edge from parent[draw=none] {}}
%      child {node {} edge from parent[draw=none] {}}
%      child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
%      child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
%      child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
%      child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
%    }
%  }
%  child {node {} edge from parent[draw=none] {}}
%  child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
%    child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
%    child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
%    child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
%    child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
%  }
%  child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
%  child {node (H5) [label={A}] [fill=yellow,circle] {}  
%    child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
%    child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
%  };
%  \draw[dashed] (H5) -> (she) ;
%
%  \com{
%  child {node (H1) [label={\#8}] [fill=black,circle] {}
%    child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
%      %child {node {to Paris} edge from parent node[right] {$A$}}
%      edge from parent node[left] {$H$}
%    }
%    child {node (H2) [label={\#9}] [fill=black,circle] {}
%      child {node  {} edge from parent[draw=none]}
%      child {node  {} edge from parent[draw=none]}
%      child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
%      child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
%      child {node [label={\#10}] [fill=black,circle] {}
%        child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
%        child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
%        edge from parent node[right] {$A$}}
%      %child {node {to Paris} edge from parent node[right] {$A$}}
%      edge from parent node[left] {$H$}
%    };
%    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
%    }
%  \end{tikzpicture}
  \\
  \end{adjustbox}
  \adjustbox{width=\textwidth,center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}

  \caption{\label{fig:ucca_example2}
    Sample UCCA annotation of a source sentence, translation (below in italics), 
    and translation judgements over the source units, marked with A,B,R,O,G labels. Yellow/blue marks
    nodes annotated with A/B, respectively.
    In our experiments, the translation is in German, Romaninan, Polish or Czech.
    ``became a passion'' is marked as atomic, as it is a multi-word expression.
    The dashed line indicates that ``she'' is also a child of the unit ``greatly improved''.
    UCCA categories, and alignment between source and translation are omitted for brevity.}

\end{figure*}

\paragraph{Translation Evaluation.}
The basic strategy for computing HUME is to traverse the semantic units
of the source sentence, which correspond to the different arguments and relations expressed
in the text, and to mark the extent to which they have been correctly translated.
HUME aggregates the judgements of the users into a composite score, 
which reflects the overall extent to which the semantic content of $s$ is preserved in $t$.
